Who does big team science?

### 2024-11-12 manuscript_definition.Rmd
updating with estimates over time need to look at nonlinear models

```{r setup, include = FALSE}
knitr::opts_knit$set(echo = FALSE, warning = FALSE, message = FALSE, include = FALSE, error = FALSE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
library(tidyr)
library(MOTE)
library(MBESS)
library(patchwork)
library(ggplot2)
library(ggwordcloud)
library(figpatch)
library(RColorBrewer)
library(latex2exp)
library(patchwork)

@@

# things to import
var_list <- c("author_stats", "paper_stats")

@@

## RQ1: Defining BTS

@@

##rq1b

>>>>

```{r setup, include = FALSE}
knitr::opts_knit$set(echo = FALSE, warning = FALSE, message = FALSE, include = FALSE, error = FALSE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
library(tidyr)
library(MOTE)
library(MBESS)
library(patchwork)
library(ggplot2)
library(ggwordcloud)
library(figpatch)
library(RColorBrewer)
library(latex2exp)
library(patchwork)
library(broom)
library(minpack.lm)

options(scipen = 99)

@@

# things to import
var_list <- c("author_stats", "paper_stats", "author_paper_year")

@@

## RQ1A: Defining BTS

@@

## RQ1B: Changes over Time

SEE IF YOU CAN GET ALL THE NUMBERS SOME ARE MISSING

```{r}
temp <- DF$author_paper_year %>% 
  filter(SubjectArea != "Multidisciplinary") %>% 
  filter(Year < 2024)

# temp %>% 
#   group_by(SubjectArea, Year, group) %>% 
#   summarize(n = n())

p1 <- ggplot(temp %>% 
         filter(group == "regular"), aes(x = Year, y = Number_Papers, colour = SubjectArea)) + 
  geom_point() + 
  theme_minimal() + 
  theme(legend.position = "none")

p2 <- ggplot(temp %>% 
         filter(group == "big"), aes(x = Year, y = Number_Papers, colour = SubjectArea)) + 
  geom_point() + 
  theme_minimal() + 
  theme(legend.position = "bottom")

p1 | p2
```

```{r}
group <- unique(temp$group)
subjarea <- unique(temp$SubjectArea)
corr.results <- list()

for (group_label in group){
  for (SA in subjarea){
    stuff <- temp %>% 
      filter(group == group_label) %>% 
      filter(SubjectArea == SA) 
    # Attempt with nlsLM for more robust optimization
    fit <- nlsLM(Number_Papers ~ a * exp(r * Year), 
             start = list(a = 0.2, r = 0.05), 
             data = stuff)
    corr.results[[paste0(group_label, "_", SA)]] <- tidy(fit)

  }
}

corr.DF <- bind_rows(corr.results) %>% 
  mutate(group = rep(group, each = 8)) %>% 
  mutate(SubjectArea = c(
    rep(subjarea, each = 2),
    rep(subjarea, each = 2)
    ))

ggplot(corr.DF, aes(x = SubjectArea, y = estimate, color = group)) + 
  geom_point() +
  theme_minimal() + 
  geom_linerange(aes(ymin = conf.low, ymax = conf.high))
```

In the exponential model ￼, the parameters ￼ and ￼ have specific interpretations:
	1.	Parameter ￼ (Initial Value or Scale):
	•	￼ represents the initial value or the scaling factor of the exponential function. It indicates the starting level of the dependent variable (in this case, Number_Papers) when the Year is at its baseline (e.g., the first year in your dataset or zero if Year is centered).
	•	A larger value of ￼ would mean a higher starting point for the number of papers.
	2.	Parameter ￼ (Growth Rate):
	•	￼ is the growth rate parameter. It indicates how quickly the number of papers grows over time.
	•	If ￼ is positive, the model shows exponential growth, meaning the number of papers increases over time at an accelerating rate.
	•	If ￼ is negative, the model would represent exponential decay, suggesting that the number of papers decreases over time.
	•	The magnitude of ￼ affects the steepness of the growth or decay curve, with larger values (in absolute terms) indicating a more rapid change.

Interpretation Example:
	•	If ￼ and ￼, then:
	•	The starting number of papers is about 2 (when Year is zero or the baseline year).
	•	The number of papers grows by about ￼ per unit of Year, as ￼ implies a growth rate of ￼ per year.
	•	If ￼, the model would predict a constant number of papers over time, as the exponential term ￼ becomes 1.

Let me know if you’d like help with the interpretation for specific values in your fitted model.
